A Documentary History of \\ the Nock Combinator Calculus

### 2025-07-06 mss.tex
Post

\begin{quote}
I have not really worked with combinator models, but my general impression is that it takes essentially an infinite amount of syntactic sugar to turn them into a programming language. \texttt{U} certainly takes some sweetener, but not, I think, as much.  (Curtis Yarvin, 2006)
\end{quote}

\sloppy
The earliest extant Nock is \texttt{U}, a proto-Nock posted to the \textit{Lambda the Ultimate} blog in 2006 (\citet{Yarvin2006a}; \citet{Yarvin2006}).\footnote{Curtis Yarvin was consulted for elements of this history.  Unfortunately many elements of the original prehistory of Nock appear to be lost to the sands of time on unrecoverable hard drives.}  The draft is versioned 0.15; subsequent evidence indicates that this is a downward-counting kelvin-versioned document already.  The full specification is reproduced in Listing~\ref{lst:u}.\footnote{The original text has been slightly modified for print.}
%Yarvin2006a, http://lambda-the-ultimate.org/node/1269
%Yarvin2006, https://web.archive.org/web/20060701070718/http://urbit.sourceforge.net/u.txt

@@

\begin{lstlisting}[style=listingcode]
   [name]   [pattern]            [definition]
    (I)      (I $a)               $a
    (K)      (K $a $b)            $b
    (S)      (S $a $b $c)         ($a $c ($b $c))
\end{lstlisting}

>>>>

\begin{quote}
I have not really worked with combinator models, but my general impression is that it takes essentially an infinite amount of syntactic sugar to turn them into a programming language. \texttt{U} certainly takes some sweetener, but not, I think, as much.  (\patp{sorreg-namtyv}\footnote{\emph{Avant la lettre.}}, 2006)
\end{quote}

\sloppy
The earliest extant Nock is \texttt{U}, a proto-Nock posted to the \textit{Lambda the Ultimate} blog in 2006 (\citet{Yarvin2006a}; \citet{Yarvin2006}).\footnote{Curtis Yarvin was consulted for elements of this history.  Unfortunately many elements of the original prehistory of Nock appear to be lost to the sands of time on unrecoverable hard drives.}  The draft is versioned 0.15; subsequent evidence indicates that this is a downward-counting kelvin-versioned document already.  The full specification is reproduced in Listing~\ref{lst:u}.
%Yarvin2006a, http://lambda-the-ultimate.org/node/1269
%Yarvin2006, https://web.archive.org/web/20060701070718/http://urbit.sourceforge.net/u.txt

@@

\begin{lstlisting}[style=listingblock]
   [name]   [pattern]            [definition]
    (I)      (I $a)               $a
    (K)      (K $a $b)            $b
    (S)      (S $a $b $c)         ($a $c ($b $c))
\end{lstlisting}
